---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/qhelpr)](https://cran.r-project.org/package=qhelpr)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/qhelpr.svg?branch=master)](https://travis-ci.org/ijlyttle/qhelpr)

# qhelpr

One purpose of an API client in R is to let you work in the R world and for the client translate to the remote world. In many cases, parameters for http queries are formatted differently from R: 

  - logicals are expressed as `"true"`/`"false"`, 
  - time durations are specified in ms (R uses difftime, or lubridate durations), 
  - vectors are expressed using comma-delimited strings. 
  
The goal of this package is to make that translation process easier.

## Installation

You can install qhelpr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/qhelpr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
