---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/qfmtr)](https://cran.r-project.org/package=qfmtr)
[![Travis-CI Build Status](https://travis-ci.org/ijlyttle/qfmtr.svg?branch=master)](https://travis-ci.org/ijlyttle/qfmtr)
[![Coverage Status](https://img.shields.io/codecov/c/github/ijlyttle/qfmtr/master.svg)](https://codecov.io/github/ijlyttle/qfmtr?branch=master)

# qfmtr

One purpose of an API client in R is to let you work in the R world and for the client translate to the remote world. In many cases, parameters for http queries are formatted differently from R: 

  - logicals are expressed: `"true"`/`"false"` 
  - time durations are specified in ms (R uses difftime, or lubridate durations)
  - vectors are expressed using comma-delimited strings. 
  
The goal of this package is to make that translation process easier.

## Installation

You can install qfmtr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ijlyttle/qfmtr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library("lubridate")
library("qfmtr")

query_params <- list(
  delay = dseconds(3),
  print = TRUE,
  next_steps = c("collate", "send"),
  number = 20
)

qfmt(query_params)
```

Here's where it can be handy:

```{r httr}
library("httr")

url <- parse_url("https://useful.site.com/service")

url$query <- qfmt(query_params)

build_url(url)
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
